Measuring Perceptions and Preferences for Meritocracy

### 2021-09-15 paper.Rmd
Ajustes edición Checklistsjr
 +  Se crean algunos archivos de imagen, para dejar en png todo lo que aparece en el pdf.

+  Se cambian los nombres de los archivos según la nomesclatura del [Checklist](https://docs.google.com/spreadsheets/d/1O8GbZ07JKsqoukfPmQ6ugieUS5mXB24alwzlNrwRIFs/edit#gid=0) "Name your figure files with "Fig" and the figure number, e.g., Fig1.eps."

+ se indican las partes de las figuras con minusculas

+ Se cambia figura por Fig.  en el titulo.

Por ahora no pude resolver dos problemas. No puedo poner en negrita Fig. 1 en el titulo de las figuras.  y por otro no puedo elim

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
author: "Juan Carlos Castillo, Julio Iturra, Luis Maldonado, Francisco Meneses & Jorge Atria <br><br>"
abstract: "Economic and social inequalities have generated growing concerns and crises across contemporary societies. One of the mechanisms proposed by social sciences to explain the persistence of inequality is the belief in meritocracy, which would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel and characterized by diverse conceptualization and measures that make the findings and their interpretation rather inconsistent. Most of the studies in the area have relied upon secondary data to operationalize meritocracy, with a wide variation in the use and interpretation of the same survey items. Taking into account the extant literature that uses measures of meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding conceptualization and operationalization. Based on this critical analysis, we propose a conceptual framework for studying perceptions and preferences for meritocracy and non-meritocracy, which is then tested through confirmatory analysis using ISSP (International Social Survey Programme) data as well as a novel survey designed specifically with this purpose (N=2,141). Our results support the conceptual framework and its operationalizarion, although with a better fit for the proposed scale than for the ISSP survey. Our discussion highlights the importance of considering different dimensions in order to advance in the study of meritocracy."
output:
  bookdown::pdf_document2:
     template: null
     toc: false
     number_sections: false
  bookdown::html_document2:
    number_sections: false
  bookdown::word_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - input/bib/meritocracy.bib
csl: input/bib/apa7-singlespace.csl  
editor_options:
  chunk_output_type: console
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{titlesec}
  - \titleformat{\paragraph}
    {\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
    \titlespacing*{\paragraph}
    {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
always_allow_html: true # for word output
fontsize: 10pt
---

@@

```{r merit-model, echo=FALSE, fig.cap = "Model of perception and preferences for meritocracy and non-meritocracy", fig.align='center'}
 knitr::include_graphics("input/images/generalf.png")
```

@@

```{r desc-issp, eval=FALSE, include=FALSE, results='asis'}
  load(file = "input/data/proc/data_s1.RData")
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(dplyr, psych, knitr, kableExtra)
  table_format = if(knitr::is_html_output()) { #conditional instructions for kable
    "html" #if html set "html" in format
  } else if(knitr::is_latex_output()) {
    "latex"#if latex set "latex" in format
  }

@@

  # Declare ggplot2 features
  ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                             colour = "gray85"),
                                    panel.border = ggplot2::element_blank(),
                                    axis.text.y = ggplot2::element_text(size = 13,
                                                                        hjust = 1),
                                    title = ggplot2::element_text(size = 13,
                                                                  face = "bold"),
                                    legend.text = ggplot2::element_text(size = 12),
                                    plot.caption = ggplot2::element_text(size = 10,
                                                                         face = "plain",
                                                                         hjust = 1)))
  #Plot 1: Perception meritocratic
  p1<- likert_issp %>%
    dplyr::select(hwork_r:ambition_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "Perception meritocratic",
                          geom.size = c(0.62),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE) +
    ggplot2::theme(legend.position = "none")
  #Plot 2: Perception Non-meritocratic
  p2<-likert_issp %>%
    dplyr::select(wealthy_r:polcone_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "Perception Non-meritocratic",
                          geom.size = c(0.9),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE)  +
    ggplot2::theme(legend.position = "none")
  #Plot 3: Preference meritocratic
  p3<-likert_issp %>%
    dplyr::select(welljob_r:hardjob_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "Preference meritocratic",
                          geom.size = c(0.62),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE) +
    ggplot2::theme(legend.position = "none")
  #Plot 4: Preference Non-meritocratic
  p4<-likert_issp %>%
    dplyr::select(family_r:child_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "Preference Non-meritocratic",
                          geom.size = c(0.62),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE) +
    ggplot2::theme(legend.position = "none")

@@

```{r likert-issp,fig.height=11,fig.width=11,fig.cap="Distribution of responses in the ISSP meritocracy items", out.width='80%'}
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(cowplot, dplyr)
  #Final plot
  cowplot::add_sub(
    cowplot::plot_grid(p1,p2,p3,p4,leg, #plot 1,2,3,4 and legend (bottom)
      align = "hv",
      axis = "a",
      nrow = 5, #5 plots
      ncol = 1, #1 column
      rel_heights = c(1,2,1,1,0.25) #fig size within plot
      ),
    label = paste0(
      "Source: Authors calculation based on International Social Survey Programme - Social Inequality 2009",
      " (n=",dim(likert_issp)[1],")"
      ),        # Caption: source and sample size
    size = 10,  # Caption font size
    hjust = 0.25# Caption align
    ) %>%
    cowplot::ggdraw()
```

@@

```{r corr-issp,fig.cap = "Perceptions and preferences for ISSP  meritocracy items' polychoric correlations", fig.align='center',fig.height=6,fig.width=8}
  load(file = "input/data/proc/data_s1.RData")
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(dplyr, corrplot, lavaan)
  # create polychoric correlation matrix
  cor_issp<-
    data_s1 %>%
    dplyr::select(hwork,ambition,wealthy,pareduc,
                  race,gender,people,polcone,
                  welljob,hardjob,family,child) %>%
    lavaan::lavCor(., ordered=names(.))
  diag(cor_issp) = NA #set diagonal values to NA
  # Set Row names of the matrix
  rownames(cor_issp) <- c("A. Hard work",
                         "B. Having ambition",
                         "C. Wealthy family",
                         "D. Educated parents",
                         "E. Race",
                         "F. Gender",
                         "G. Knowing people",
                         "H. Political connections",
                         "I. Well job",
                         "J. Hard job",
                         "K. Support family",
                         "L. Has children")
  #set Column names of the matrix
  colnames(cor_issp) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)",
                         "(H)", "(I)","(J)","(K)","(L)")

  #Plot the matrix using corrplot
  corrplot::corrplot(cor_issp,
    method = "color",
    addCoef.col = "#000390",
    type = "upper",
    tl.col = "black",
    col=colorRampPalette(c("white","#0068DC"))(12),
    bg = "white",
    na.label = "-")
```

@@

```{r meas02-issp, echo=FALSE, fig.cap = "Descriptive plot", fig.align='center',fig.cap="Confirmatory factor analysis of the ISSP indicators of Perceptions and Preferences for Meritocracy"}
 knitr::include_graphics('output/images/cfa_issp_study1.PNG')
```

@@

```{r appmod, echo=FALSE, fig.cap = "Survey flow", fig.align='center'}
 knitr::include_graphics('output/images/app_mod.png')
```

@@

  #Plot 1: Perception
  p1<-
    dplyr::select(dat_likert_s2,perc_effort_r:perc_netw_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        title = c("Perceptions"),
                        geom.size = 0.8,
                        axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                        catcount = 4,
                        cat.neutral = 3,
                        grid.range  =  c (1.2 , 1.2),
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) +
    ggplot2::theme(legend.position = "none")

  #Plot 2: Preferences
  p2<-
    dplyr::select(dat_likert_s2,pref_effort_r:pref_netw_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        title = c("Preferences"),
                        geom.size = 0.8,
                        axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                        catcount = 4,
                        cat.neutral = 3,
                        grid.range  =  c (1.2 , 1.2),
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE)  +
    ggplot2::theme(legend.position = "none")

@@

```{r plotlikert, echo=FALSE, fig.align='center', fig.cap="Distribution of responses in the Merit Scale items", fig.height=8, fig.width=11}
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(cowplot)
  #Final plot
  cowplot::add_sub(
    cowplot::plot_grid(p1,p2,leg, #plot 1,2 and legend (bottom)
      align = "hv",
      axis = "a",
      nrow = 3, #2 plots
      ncol = 1, #1 column
      rel_heights = c(1,1,0.25) #fig size within plot
      ),
    label = paste0("Source: Authors calculations based on Study 2 sample"," (n=",dim(na.omit(dat_likert_s2))[1],")"
      ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.15# Caption align
    ) %>%
    cowplot::ggdraw()
```

@@

```{r corpoly, echo=FALSE, fig.cap = "Perceptions and preferences for meritcoracy items' polychoric correlations", fig.align='center'}
  if (!require("pacman")) install.packages("pacman")
  load(file = "input/data/proc/data_s2.RData")
  pacman::p_load(dplyr, corrplot, lavaan)
  # generate polychoric matrix
  cor_s2<- data_s2 %>%
    dplyr::select(perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw) %>%
    lavaan::lavCor(., ordered=names(.))

@@

  corrplot::corrplot(cor_s2,
    method = "color",
    addCoef.col = "#000390",
    type = "upper",
    tl.col = "black",
    col=colorRampPalette(c("white","#0068DC"))(8),
    bg = "white",
    na.label = "-")
```

@@

```{r meas02, echo=FALSE, fig.cap = "Confirmatory factor analysis of the Perceptions and Preferences for Meritocracy Scale", fig.align='center'}
 # estimation for diagram: summary(fit_cfa3, standardized = TRUE, fit.measures=TRUE)
 knitr::include_graphics('output/images/cfa_randomized_study2.png')
```

>>>>

---
title: "Measuring Perceptions and Preferences for Meritocracy"
css: "custom.css"
linestretch: '1.5'
link-citations: yes
author: "Juan Carlos Castillo, Julio Iturra, Luis Maldonado, Francisco Meneses & Jorge Atria <br><br>"
abstract: "Economic and social inequalities have generated growing concerns and crises across contemporary societies. One of the mechanisms proposed by social sciences to explain the persistence of inequality is the belief in meritocracy, which would legitimize economic disparities based on differences in effort and talent. Despite its wide use as a concept, empirical research on meritocracy is relatively novel and characterized by diverse conceptualization and measures that make the findings and their interpretation rather inconsistent. Most of the studies in the area have relied upon secondary data to operationalize meritocracy, with a wide variation in the use and interpretation of the same survey items. Taking into account the extant literature that uses measures of meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding conceptualization and operationalization. Based on this critical analysis, we propose a conceptual framework for studying perceptions and preferences for meritocracy and non-meritocracy, which is then tested through confirmatory analysis using ISSP (International Social Survey Programme) data as well as a novel survey designed specifically with this purpose (N=2,141). Our results support the conceptual framework and its operationalizarion, although with a better fit for the proposed scale than for the ISSP survey. Our discussion highlights the importance of considering different dimensions in order to advance in the study of meritocracy."
output:
  bookdown::pdf_document2:
     template: null
     toc: false
     number_sections: false
  bookdown::html_document2:
    number_sections: false
  bookdown::word_document2:
    number_sections: false
linkcolor: blue
bibliography:
  - input/bib/meritocracy.bib
csl: input/bib/apa7-singlespace.csl  
editor_options:
  chunk_output_type: console
geometry: margin=0.78in
header-includes:
  # - \usepackage[spanish,es-tabla,es-nodecimaldot]{babel}
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage[figurename=Fig.]{caption}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{titlesec}
  - \titleformat{\paragraph}
    {\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
    \titlespacing*{\paragraph}
    {0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
always_allow_html: true # for word output
fontsize: 10pt
---

@@

```{r merit-model, echo=FALSE, fig.cap = "Model of perception and preferences for meritocracy and non-meritocracy", fig.align='center'}
 knitr::include_graphics("input/images/Fig1.generalf.png")
```

@@

```{r desc-issp, eval=FALSE, include=FALSE, results='asis'}

  load(file = "input/data/proc/data_s1.RData")
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(dplyr, psych, knitr, kableExtra)
  table_format = if(knitr::is_html_output()) { #conditional instructions for kable
    "html" #if html set "html" in format
  } else if(knitr::is_latex_output()) {
    "latex"#if latex set "latex" in format
  }

@@

  # Declare ggplot2 features
  ggplot2::theme_set(ggplot2::theme(panel.background = ggplot2::element_rect(fill = "gray85",
                                                                             colour = "gray85"),
                                    panel.border = ggplot2::element_blank(),
                                    axis.text.y = ggplot2::element_text(size = 13,
                                                                        hjust = 1),
                                    title = ggplot2::element_text(size = 13,
                                                                  face = "bold"),
                                    legend.text = ggplot2::element_text(size = 12),
                                    plot.caption = ggplot2::element_text(size = 10,
                                                                         face = "plain",
                                                                         hjust = 1)))
  #Plot 1: Perception meritocratic
  p1<- likert_issp %>%
    dplyr::select(hwork_r:ambition_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "a. Perception meritocratic",
                          geom.size = c(0.62),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE) +
    ggplot2::theme(legend.position = "none")
  #Plot 2: Perception Non-meritocratic
  p2<-likert_issp %>%
    dplyr::select(wealthy_r:polcone_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "b. Perception Non-meritocratic",
                          geom.size = c(0.9),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE)  +
    ggplot2::theme(legend.position = "none")
  #Plot 3: Preference meritocratic
  p3<-likert_issp %>%
    dplyr::select(welljob_r:hardjob_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "c. Preference meritocratic",
                          geom.size = c(0.62),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE) +
    ggplot2::theme(legend.position = "none")
  #Plot 4: Preference Non-meritocratic
  p4<-likert_issp %>%
    dplyr::select(family_r:child_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        grid.range  =  c (1.2 , 1.2),
                        title = "d. Preference Non-meritocratic",
                          geom.size = c(0.62),
                          catcount = 5,
                          expand.grid = T,
                          values  =  "sum.outside",
                          reverse.colors = T,
                          reverse.scale = F,
                          show.n = FALSE) +
    ggplot2::theme(legend.position = "none")

@@

```{r likert-issp,fig.height=11,fig.width=11,fig.cap="Distribution of responses in the ISSP meritocracy items", out.width='80%'}

#dev.copy(png,'output/images/Fig2.plotlikert-study1.png') # save image

  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(cowplot, dplyr)
  #Final plot
  cowplot::add_sub(
    cowplot::plot_grid(p1,p2,p3,p4,leg, #plot 1,2,3,4 and legend (bottom)
      align = "hv",
      axis = "a",
      nrow = 5, #5 plots
      ncol = 1, #1 column
      rel_heights = c(1,2,1,1,0.25) #fig size within plot
      ),
    label = paste0(
      "Source: Authors calculation based on International Social Survey Programme - Social Inequality 2009",
      " (n=",dim(likert_issp)[1],")"
      ),        # Caption: source and sample size
    size = 10,  # Caption font size
    hjust = 0.25# Caption align
    ) %>%
    cowplot::ggdraw()
#dev.off()
```

@@

```{r corr-issp,fig.cap = "Perceptions and preferences for ISSP  meritocracy items' polychoric correlations", fig.align='center',fig.height=6,fig.width=8}

#dev.copy(png,'output/images/Fig3.plotcor-sutdy1.png') # save image

  load(file = "input/data/proc/data_s1.RData")
  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(dplyr, corrplot, lavaan)
  # create polychoric correlation matrix
  cor_issp<-
    data_s1 %>%
    dplyr::select(hwork,ambition,wealthy,pareduc,
                  race,gender,people,polcone,
                  welljob,hardjob,family,child) %>%
    lavaan::lavCor(., ordered=names(.))
  diag(cor_issp) = NA #set diagonal values to NA
  # Set Row names of the matrix
  rownames(cor_issp) <- c("A. Hard work",
                         "B. Having ambition",
                         "C. Wealthy family",
                         "D. Educated parents",
                         "E. Race",
                         "F. Gender",
                         "G. Knowing people",
                         "H. Political connections",
                         "I. Well job",
                         "J. Hard job",
                         "K. Support family",
                         "L. Has children")
  #set Column names of the matrix
  colnames(cor_issp) <-c("(A)", "(B)","(C)","(D)","(E)","(F)","(G)",
                         "(H)", "(I)","(J)","(K)","(L)")

  #Plot the matrix using corrplot
  corrplot::corrplot(cor_issp,
    method = "color",
    addCoef.col = "#000390",
    type = "upper",
    tl.col = "black",
    col=colorRampPalette(c("white","#0068DC"))(12),
    bg = "white",
    na.label = "-")

#dev.off()

```

@@

```{r meas02-issp, echo=FALSE, fig.cap = "Descriptive plot", fig.align='center',fig.cap="Confirmatory factor analysis of the ISSP indicators of Perceptions and Preferences for Meritocracy"}
 knitr::include_graphics('output/images/Fig4.cfa_issp_study1.PNG')
```

@@

```{r appmod, echo=FALSE, fig.cap = "Survey flow", fig.align='center'}
 knitr::include_graphics('output/images/Fig5.app_mod.png')
```

@@

  #Plot 1: Perception
  p1<-
    dplyr::select(dat_likert_s2,perc_effort_r:perc_netw_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        title = c("a. Perceptions"),
                        geom.size = 0.8,
                        axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                        catcount = 4,
                        cat.neutral = 3,
                        grid.range  =  c (1.2 , 1.2),
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE) +
    ggplot2::theme(legend.position = "none")

  #Plot 2: Preferences
  p2<-
    dplyr::select(dat_likert_s2,pref_effort_r:pref_netw_r) %>%
    sjPlot::plot_likert(geom.colors = "PuBu",
                        title = c("b. Preferences"),
                        geom.size = 0.8,
                        axis.labels = c("Effort", "Talent", "Rich Parents", "Contacts"),
                        catcount = 4,
                        cat.neutral = 3,
                        grid.range  =  c (1.2 , 1.2),
                        values  =  "sum.outside",
                        reverse.colors = T,
                        reverse.scale = F,
                        show.n = FALSE)  +
    ggplot2::theme(legend.position = "none")

@@

```{r plotlikert, echo=FALSE, fig.align='center', fig.cap="Distribution of responses in the Merit Scale items", fig.height=8, fig.width=11}

#dev.copy(png,'output/images/Fig6.plotlikertmerit-scale.png') # save image

  if (!require("pacman")) install.packages("pacman")
  pacman::p_load(cowplot)
  #Final plot
  cowplot::add_sub(
    cowplot::plot_grid(p1,p2,leg, #plot 1,2 and legend (bottom)
      align = "hv",
      axis = "a",
      nrow = 3, #2 plots
      ncol = 1, #1 column
      rel_heights = c(1,1,0.25) #fig size within plot
      ),
    label = paste0("Source: Authors calculations based on Study 2 sample"," (n=",dim(na.omit(dat_likert_s2))[1],")"
      ),        # Caption: source and sample size
    size = 12,  # Caption font size
    hjust = -0.15# Caption align
    ) %>%
    cowplot::ggdraw()
  #dev.off()

```

@@

```{r corpoly, echo=FALSE, fig.cap = "Perceptions and preferences for meritcoracy items' polychoric correlations", fig.align='center'}

#dev.copy(png,'output/images/Fig6.plotcor-sutdy2.png') # save image  
  if (!require("pacman")) install.packages("pacman")
  load(file = "input/data/proc/data_s2.RData")
  pacman::p_load(dplyr, corrplot, lavaan)
  # generate polychoric matrix
  cor_s2<- data_s2 %>%
    dplyr::select(perc_effort,perc_talent,perc_wpart,perc_netw,pref_effort,pref_talent,pref_wpart,pref_netw) %>%
    lavaan::lavCor(., ordered=names(.))

@@

  corrplot::corrplot(cor_s2,
    method = "color",
    addCoef.col = "#000390",
    type = "upper",
    tl.col = "black",
    col=colorRampPalette(c("white","#0068DC"))(8),
    bg = "white",
    na.label = "-")
#dev.off()
```

@@

```{r meas02, echo=FALSE, fig.cap = "Confirmatory factor analysis of the Perceptions and Preferences for Meritocracy Scale", fig.align='center'}
 # estimation for diagram: summary(fit_cfa3, standardized = TRUE, fit.measures=TRUE)
 knitr::include_graphics('output/images/Fig8.cfa_randomized_study2.png')
```
